### 2019-07-25 5_evaluation.tex
More space tweaking.

In theory, any system should be able to hit peak performance as long as
the kernels are well-written and of sufficiently large granularity. In
practice, achieving peak performance is tricky, and many subtle pitfalls of implementation or configuration can easily lead to poor performance. Unfortunately, peak performance is also frequently skipped in evaluations of
runtime system overhead. However, verifying that peak performance is
achieved is important to ensuring that evaluations of overhead and
efficiency are well-grounded.

\input{e1_flops}
\input{e2_efficiency}

@@

The vast majority of systems achieve or nearly achieve peak FLOP/s. Some
systems reserve a number of cores (usually 1 or 2) for internal
runtime usage; these systems take a minor hit in peak FLOP/s compared
to systems which share all cores between the application and runtime. Some of the
higher overhead systems struggle to achieve peak FLOP/s, though in most cases
the curves suggest that performance would continue to improve if we
were to run larger problem sizes. Unfortunately, the excessive
computational cost of running such tests makes this prohibitively
expensive. For example, the Spark job in
this case ran for over 6 hours.

@@

We observe in the results that the baseline overheads of different
systems vary by over 5 orders of magnitude. It is worth
remembering when considering this metric that this is a \emph{minimum}
effective task granularity. Therefore applications with an average
task granularity of \emph{at least} this value can usually be expected
to execute efficiently. Typical task granularities will
generally be determined by the application domain being
considered. Most notably, for large-scale data analytics workloads, the higher METG values observed for Spark and
TensorFlow are sufficient. In contrast, for high-performance
scientific simulations, task granularities in the millisecond range
are useful, as such applications communicate (e.g., for halo
exchanges) much more frequently.

>>>>

In theory, any system should achieve peak performance if
the kernels are well-tuned and of sufficiently large granularity. In
practice, many subtle pitfalls of implementation or configuration can easily lead to poor performance. Verifying that peak performance is
achieved helps to ensure that evaluations of overhead and
efficiency are well-grounded.

\input{e1_flops}
\input{e2_efficiency}
\input{e7_bytes}

@@

Most systems achieve or nearly achieve peak FLOP/s. Some
systems reserve a number of cores (usually 1 or 2) for internal
runtime usage; these systems take a minor hit in peak FLOP/s compared
to systems which share all cores between the application and runtime. Some of the
higher overhead systems struggle to achieve peak FLOP/s, though in most cases
the curves suggest that performance would continue to improve if we
were to run larger problem sizes. Unfortunately, the excessive
computational cost of running such tests makes this prohibitively
expensive. For example, the Spark job in
this case ran for over 6 hours.

@@

We observe that the baseline overheads of different
systems vary by over 5 orders of magnitude. It is worth
remembering when considering this metric that this is a \emph{minimum}
effective task granularity. Therefore applications with an average
task granularity of \emph{at least} this value can usually be expected
to execute efficiently. Typical task granularities will
generally be determined by the application domain being
considered. Most notably, for large-scale data analytics workloads, the higher METG values observed for Spark and
TensorFlow are sufficient. In contrast, for high-performance
scientific simulations, task granularities in the millisecond range
are useful, as such applications communicate (e.g., for halo
exchanges) much more frequently.
